Communication complexity: Chapter 3 \\ Distributional communication complexity

### 2019-01-25 CS860-CommunicationComplexity/assignments/Chapter3.tex
submission

\begin{proof}
\replacethistext{Enter your proof here.}
\end{proof}

@@

$$1= \sum_{i=1}^t \mu(R_i) = \sum_{i=1}^t \mu(R_i \cap f^{-1}(0)) + \mu(R_i\cap f^{-1}(1)) \geq \alpha - t \beta +\mu(f^{-1}(1))$$
Thus
$$t \geq \frac{\alpha + \mu(f^{-1}(1)) -1}{\beta}.$$
Now we claim that 
$$\alpha + \mu(f^{-1}(1)) -1 \geq \alpha\cdot \mu(f^{-1}(1)) -\epsilon.$$
This claim is equivalent to
$$1-\epsilon \leq \alpha(\mu(f^{-1}(0))) +\mu(f^{-1}(1)).$$
This holds since $1-\epsilon$ is the probability of success \replacethistext{(I didn't have time to formalize)}.
\end{proof}

@@

\begin{proposition}[\textsc{Bonus}]
Every rectangle $R = A \times B \subseteq 2^{[n]} \times 2^{[n]}$
that satisfies 
\[
\Pr_{(S,T) \in R}[ S \cap T = \emptyset ] \ge 1-\alpha
\]
has size bounded by
\[
|A| \le 2^{-\delta \sqrt{n}} \binom{n}{\sqrt{n}}
\qquad \mbox{or} \qquad
|B| \le 2^{-\delta \sqrt{n}} \binom{n}{\sqrt{n}}.
\]
\end{proposition}

>>>>

\begin{proof}
I'm not really sure what the right distribution to take is, but intuitively I want to distribute the probability mass evenly between $(x,y)$ pairs with $x\neq y$ and pairs with $x=y$ so Alice and Bob have to exchange some bits to do better than guessing. From the matrix of this function I want half the probability mass uniformly distributed on the diagonal, and half uniformly distributed on all off-diagonal entries.
\end{proof}

@@

$$1= \sum_{i=1}^t \mu(R_i) = \sum_{i=1}^t \mu(R_i \cap f^{-1}(0)) + \mu(R_i\cap f^{-1}(1)) \geq \alpha - t \beta +\mu(f^{-1}(1))$$
Thus
$$t \geq \frac{\alpha + \mu(f^{-1}(1)) -1}{\beta}.$$
Now we claim that 
$$\alpha + \mu(f^{-1}(1)) -1 \geq \alpha\cdot \mu(f^{-1}(1)) -\epsilon.$$
This claim is equivalent to
$$1-\epsilon \leq \alpha(\mu(f^{-1}(0))) +\mu(f^{-1}(1)).$$
Since 
$$\alpha(\mu(f^{-1}(0))) +\mu(f^{-1}(1)) = 1-(1-\alpha) \mu(f^{-1}(0))$$
the claim holds since the probability of failure is at least $(1-\alpha)f^{-1}(0)$ \replacethistext{(I didn't have time to formalize)}.
\end{proof}

@@

\begin{proposition}[\textsc{Bonus}]
For every $\alpha >0$ there exists $\delta>0$ such that every rectangle $R = A \times B \subseteq 2^{[n]} \times 2^{[n]}$
that satisfies 
\[
\Pr_{(S,T) \in R}[ S \cap T = \emptyset ] \ge 1-\alpha
\]
has size bounded by
\[
|A| \le 2^{-\delta \sqrt{n}} \binom{n}{\sqrt{n}}
\qquad \mbox{or} \qquad
|B| \le 2^{-\delta \sqrt{n}} \binom{n}{\sqrt{n}}.
\]
\end{proposition}
